The core transcriptome of the mammal placenta

### 2016-08-12 manuscript/manuscript.Rnw
remove ateles top 50
remove human name from diff table

        display.table <-
            display.table[,`Human Symbol`:=paste0("\\textit{",xtable.sanitize.text(`Human Symbol`),
                                                  "}")]
        # setnames(display.table,"Human Symbol","\\multicolumn{1}{p{0.5in}}{Human Symbol}")6
        setnames(display.table,"Fold Change","$\\text{log}_2$ FC")
        print(xtable(display.table,
                     display=c("s","s","s","e","g","f"),
                     align=c("c","p{0.5in}","p{1in}","r","r","r")
                     ),
              booktabs=TRUE,
              floating=FALSE,
              math.style.exponents=TRUE,
              sanitize.text.function=genes.table.sanitize,
              include.rownames=FALSE)

@@

\begin{table}
  \footnotesize
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
output.top.genes.table(top.spider.monkey.genes)
setkey(top.spider.monkey.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\smonkey}{tab:all_ateles_fusciceps_placenta}}
\label{tab:top50_spider_monkey_placenta}
\end{table}

>>>>

        display.table <-
            display.table[,`Human Symbol`:=paste0("\\textit{",xtable.sanitize.text(`Human Symbol`),
                                                  "}")]
        display.table[,`Human Name`:=NULL]
        # setnames(display.table,"Human Symbol","\\multicolumn{1}{p{0.5in}}{Human Symbol}")6
        setnames(display.table,"Fold Change","$\\text{log}_2$ FC")
        print(xtable(display.table,
                     display=c("s","s","e","g","f"),
                     align=c("c","p{0.5in}","r","r","r")
                     ),
              booktabs=TRUE,
              floating=FALSE,
              math.style.exponents=TRUE,
              sanitize.text.function=genes.table.sanitize,
              include.rownames=FALSE)

@@

% \begin{table}
%   \footnotesize
% <<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
% top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
% output.top.genes.table(top.spider.monkey.genes)
% setkey(top.spider.monkey.genes,"Gene symbol")
% @ 
% \caption{\tableexplanation{\smonkey}{tab:all_ateles_fusciceps_placenta}}
% \label{tab:top50_spider_monkey_placenta}
% \end{table}
